### 2016-07-06 abstract.tex

  Serializability is a well-understood correctness criterion that
  simplifies reasoning about the behavior of concurrent transactions
  by ensuring that transactions are \emph{isolated} from each other.
  However, enforcing serializable isolation comes at a steep cost in
  performance because it necessarily restricts opportunities to
  exploit concurrency even when such opportunities would not violate
  application-specific invariants. As a result, database systems in
  practice support, and often encourage, developers to use weaker
  alternatives. These alternatives break the strong isolation
  guarantees offered by serializable transactions to permit greater
  concurrency. Unfortunately, the semantics of weak isolation is
  poorly understood, and usually explained only informally in terms of
  low-level implementation artifacts. Consequently, verifying
  high-level correctness properties in such environments remains a
  challenging problem.

  To address this issue, we present a program logic that enables
  compositional reasoning about the behavior of concurrently executing
  weakly-isolated transactions. Notably, our development is parametric
  over a transaction's specific isolation semantics, and the
  consistency guarantees provided by the underlying data store,
  allowing it to be applicable over a range of concurrency control
  mechanisms.  Case studies and experiments on real-world applications
  demonstrate the utility of our approach, and provide strong evidence
  that weakly-isolated transactions can be placed on the same formal
  footing as their strongly-isolated serializable counterparts.

>>>>

  Serializability is a well-understood correctness criterion that
  simplifies reasoning about the behaviour of concurrent transactions
  by ensuring they are \emph{isolated} from each other while they
  execute.  However, enforcing serializable isolation comes at a steep
  cost in performance because it necessarily restricts opportunities
  to exploit concurrency even when such opportunities would not
  violate application-specific invariants. As a result, database
  systems in practice support, and often encourage, developers to use
  weaker alternatives. These alternatives break the strong isolation
  guarantees offered by serializable transactions to permit greater
  concurrency. Unfortunately, the semantics of weak isolation is
  poorly understood, and usually explained only informally in terms of
  low-level implementation artifacts. Consequently, verifying
  high-level correctness properties in such environments remains a
  challenging problem.

  To address this issue, we present a program logic that enables
  compositional reasoning about the behaviour of concurrently
  executing weakly-isolated transactions. Notably, our development is
  parametric over a transaction's specific isolation semantics, and
  the consistency guarantees provided by the underlying data store,
  allowing it to be applicable over a range of concurrency control
  mechanisms.  Case studies and experiments on real-world applications
  demonstrate the utility of our approach, and provide strong evidence
  that weakly-isolated transactions can be placed on the same formal
  footing as their strongly-isolated serializable counterparts.
